%
% *** A LIST OF REFERENCES RELATED TO PCA NEURAL NETWORKS ***
%
% The reference list below and general remarks on it in the beginning
% are given in the form of a LaTeX text file.
%
%
\documentstyle{article}
\textwidth=17cm
\textheight=24cm
\topmargin=0cm
\topskip=0.3cm
\headheight=0cm
\headsep=0cm
\oddsidemargin=-1cm
\footskip=0.5cm
\def\Romannumeral#1{\uppercase{\expandafter\romannumeral#1}}
%
\begin{document}
\title{A Collection of References on PCA Type Neural Networks}
\author{Compiled by Liu-Yue Wang and Juha Karhunen\\Helsinki 
University of Technology \\Finland}
\date{December 1, 1993}
\maketitle
%
\section*{General information}
Beginning from the next page, you will find
a collection of references on Principal Component Analysis (PCA)
neural networks and learning algorithms. In addition, it contains
references on extensions and generalizations of such networks and some
basic references on PCA and related matters. You can copy the
list freely on your own responsibility. It is published
in the form of a LaTeX file, and should be ready for compiling and 
printing with
possible minor changes needed for your output device.

The original list has been compiled by Liu-Yue Wang, a graduate student of
Prof.\ Erkki Oja, and updated by Dr. Juha Karhunen.
The list should cover fairly well the field of PCA networks,
but it is not complete and contains possibly some errors
and nonuniformity in notation.
Anyway, the reference collection should be useful for people interested in
PCA neural networks already in its present form.
- If you find errors or know relevant references lacking from the list,
you can e-mail or mail them to me:\\[1cm]
%
Juha Karhunen\\Helsinki Univ. of Technology\\
Lab. of Computer and Information Science
\\Rakentajanaukio 2 C\\SF-02150 Espoo, FINLAND\\
email: Juha.Karhunen@hut.fi
%
%
\newpage
\begin{thebibliography}{999}
\baselineskip 3mm
\itemsep=-0.15cm
\leftmargin=0cm
\rightmargin=0cm

\bibitem{Abbas92}
H.M.~Abbas and M.M.~Fahmy.
``A Neural Model for Adaptive Karhunen Lo\`{e}ve Transformation (KLT)''.
In {\em Proc. Int. Joint Conf. on Neural Networks}, Baltimore, Maryland,
June 1992, pp. II-975-980.

\bibitem{Almeida92}
L.B.~Almeida and F.M.~Silva.
``Adaptive Decorrelation''.
In I.~Aleksander and J.~Taylor (Eds.), {\em Artificial Neural
Networks, 2} (Proc. ICANN'92, Brighton, UK, September 1992), Elsevier,
1992, pp. 149-156.

\bibitem{Ambros90}
J.~Ambros-Ingerson, R.~Granger and G.~Lynch.
``Simulation of Paleocortex Performs Hierarchical Clustering''.
{\em Science}, vol. 247, 1990, pp. 1344-1348.   

\bibitem{Atick92}
J.J.~Atick.
``Could Information Theory Provide an Ecological Theory of Sensory
Processing ?''.
{\em Network}, vol. 3, 1992, pp. 213-251.

\bibitem{Atick93}
J.J.~Atick.
``Convergent Algorithm for Sensory Receptive Field Development''.
{\em Neural Computation}, vol. 5, 1993, pp. 45-60.

\bibitem{Baldi88}
P.~Baldi.
``Linear Learning: Landscapes and Algorithms''.
In D.S.~Touretzky (Ed.), {\em Advances in Neural Information Processing
Systems I}. Morgan Kaufmann, San Mateo, Calif., 1989, pp. 65-72.

\bibitem{Baldi89}
P.~Baldi and K.~Hornik.
``Neural Networks for Principal Component Analysis: Learning from
Examples Without Local Minima''.
{\em Neural Networks}, vol. 2, 1989, pp. 53-58.

\bibitem{Baldi91}
P.~Baldi and K.~Hornik.
``Back-Propagation and Unsupervised Learning in Linear Networks''.
In Y.~Chauvin and D.E.~Rumelhart (Eds.), {\em Back Propagation:
Theory, Architectures and Applications}. Lawrence Erlbaum, 1991(?).

\bibitem{Bannour91}
S.~Bannour and M.R.~Azimi-Sadjadi.
``Principal Component Extraction Using Recursive Least Squares Learning
Method''.
In {\em Proc. Int. J. Conf. on Neural Networks}, Singapore, November 1991,
vol. 3, pp. 2110-2115. 

\bibitem{Barlow89}
H.B.~Barlow.
``Unsupervised Learning''.
{\em Neural Computation}, vol. 1, 1989, pp. 295-311.

\bibitem{Basso92}
A.~Basso.
``Autoassociative Neural Networks for Image Compression: a Massively
Parallel Implementation''.
In S.Y.~Kung et al.\ (Eds.), {\em Neural Networks for Signal
Processing II} (Proc. of the 1992 IEEE-SP Workshop, Copenhagen, Denmark,
August-September 1992). IEEE Press, New York 1992, pp. 373-381.

\bibitem{Becker91}
S.~Becker.
``Unsupervised Learning Procedures for Neural Networks''.
{\em Int. J. of Neural Systems}, vol. 2, 1991, pp. 17-33.

\bibitem{Bourlard88}
H.~Bourlard and Y.~Kamp.
``Auto-Association by Multilayer Perceptrons and Singular Value
Decomposition''.
{\em Biological Cybernetics}, vol. 59, 1988, pp. 291-294.

\bibitem{Brause92}
R.~Brause.
``The Minimum Entropy Neuron - A New Building Block for Clustering
Transformations''.
In I.~Aleksander and J.~Taylor (Eds.), {\em Artificial Neural
Networks, 2} (Proc. ICANN'92, Brighton, UK, September 1992), Elsevier,
1992, pp. 1095-1098. 

\bibitem{Brause93}
R.~Brause.
``A Symmetrical Lateral Inhibition Network for PCA and Feature
Decorrelation''.
In S.~Gielen and B.~Kappen (Eds.), {\em ICANN'93 (Proc. Int. Conf.
on Artificial Neural Networks, Amsterdam, September 1993)}.
Springer-Verlag, London 1993, pp. 486-489.
 
\bibitem{Brockett91}
R.W.~Brockett.
``Dynamical Systems that Sort Lists, Diagonalize Matrices
and Solve Linear Programming Problems''.
{\em Linear Algebra Appl.}, vol. 146. 1991, pp. 79-91.

\bibitem{Brockett91b}
R.W.~Brockett.
``Dynamical Systems that Learn Subspaces''.
In {\em Mathematical System Theory: The Influence of
R.E.~Kalman}, Springer-Verlag, Berlin, 1991, pp. 579-592.

\bibitem{Carlson90}
A.~Carlson.
``Anti-Hebbian Learning in a Non-Linear Neural Network''.
{\em Biological Cybernetics}, vol. 64, 1990, pp. 171-176.

\bibitem{Carrato91}
S.~Carrato, G.~Ramponi, A.~Premoli, and G.L.~Sicuranza.
``Improved Structures Based on Neural Networks for Image Compression''.
In B.H.~Juang, S.Y.~Kung, and C.A.~Kamm (Eds.), {\em Neural
Networks for Signal Processing} (Proc. 1991 IEEE-SP Workshop, Princeton,
New Jersey, September 1991). IEEE Press, New York, 1991, pp. 493-502.

\bibitem{Carrato92}
S.~Carrato and S.~Marsi.
``Compression of Subband-Filtered Images via Neural Networks''.
In S.Y.~Kung et al. (Eds.), {\em Neural Networks for Signal Processing
II} (Proc. 1992 IEEE-SP Workshop, Copenhagen, Denmark, August-September
1992). IEEE Press, New York, 1991, pp. 382-390.
 
\bibitem{Chang93}
S.~Chang and L.-H.~Chen. 
``An Improved Learning Algorithm for Principal Component Analysis''.
In {\em Proc. of the 4th Int. Conf. on Signal 
Processing and Technology}, Calif., USA, September-October 1993.

\bibitem{Chauvin89}
Y.~Chauvin.
``Principal Component Analysis by Gradient Descent on
a Constrained Linear Hebbian Cell''.
In {\em Proc. of Int. J. Conf. on Neural Networks}, Washington D.C.,
1989, pp. I-373-380.

\bibitem{Chauvin91}
Y.~Chauvin.
``Constrained Hebbian Learning: Gradient Descent to Global
Minima in an N-dimensional Landscape'',
{\em Int. Journal of Neural Systems}, vol. 2, 1991, pp. 35-46.

\bibitem{HChen91}
H.~Chen and R.~Liu.
``An Alternative Proof of Convergence for Kung-Diamantaras APEX
Algorithm''.
In B.H.~Juang, S.Y.~Kung, and C.A.~Kamm (Eds.),
{\em Neural Networks for Signal Processing} (Proc. of 1991 IEEE-SP
Workshop, Princeton, New Jersey). IEEE Press, New York, 1991, pp. 40-49.

\bibitem{HChen92}
H.~Chen and R.-W.~Liu.
``Adaptive Distributed Orthogonalization Processing for Principal Components
Analysis''.
In {\em Proc. IEEE Int. Conf. on Acoustics, Speech, and Signal Processing},
San Francisco, March 1992, vol. II, pp. 293-296.

\bibitem{YChen92}
Y.~Chen and C.~Hou.
``High Resolution Adaptive Bearing Estimation Using a Complex-Weighted
Neural Network''.
In {\em Proc. IEEE Int. Conf. on Acoustics, Speech, and Signal Processing},
San Francisco, March 1992, vol. II, pp. 
 
\bibitem{Cichocki92}
A.~Cichocki and  R.~Unbehauen.
``Neural Networks for Computing Eigenvalues and Eigenvectors''.
{\em Biological Cybernetics}, vol. 68, 1992, pp. 155-164.

\bibitem{Cichocki93}
A.~Cichocki and R.~Unbehauen.
{\em Neural Networks for Optimization and Signal Processing}. 
J. Wiley, New York, 1993.

\bibitem{Comon90}
P.~Comon and G.H.~Golub
``Tracking a Few Extreme Singular Values and Vectors in Signal Processing''.
{\em Proceedings of the IEEE}, vol. 78, August 1990, pp. 1327-1343.

\bibitem{Cottrell87}
G.W.~Cottrell, P.W.~Munro, and D.~Zipser.
``Learning Internal Representations from Gray-Scale Images: 
An Example of Representational Programming''.
In {\em  Proc. 9th Annual Conf. of the Cognitive Science Society}, 
July 16-18, 1987, pp. 462-473.

\bibitem{Cottrell88}
G.W.~Cottrell and P.W.~Munro. 
``Principal Components of Images via Back Propagation''.
{\em Proc. of SPIE, vol. 1001: Visual Communications and Image
Processing '88}, 1988, pp. 1070-1077.

\bibitem{Moor88}
B.~De Moor, J.~Staar, and J.~Vandewalle.
``Oriented Energy and Oriented Signal to Signal Ratio Concepts in
the Analysis of Vector Sequences and Time Series''.
In E.F.~Deprettere (Ed.), {\em SVD and Signal Processing},
Elsevier (North Holland), 1988, pp.  209-232.

\bibitem{Deng93}
D.~Deng and Y.-L.~Yu.
``Using PCA Network for Image Analysis and Segementation''.
In {\em Proc. of IEEE Int. Conf. on Neural Network Application to Signal
Processing}, Singapore, August 1993. 
 
\bibitem{Diamantaras91}
K.I.~Diamantaras and S.Y.~Kung.
``An Unsupervised Neural Model for Oriented Principal Component Extraction''.
In {\em Proc. IEEE Int. Conf. on Acoustics, Speech, and
Signal Processing}, Toronto, Canada, May 1991, pp. 1049-1052.
  
\bibitem{Diamantaras92}
K.I.~Diamantaras and S.Y.~Kung.
``Multilayer Neural Networks for Reduced Rank Approximation under
Rank-Deficient Input Data''.
Accepted for publication in IEEE Trans. on Neural Networks.

\bibitem{Diamantaras93}
K.I.~Diamantaras and S.Y.~Kung.
``Compressing Moving Pictures Using the APEX Neural Principal Component
Extractor".
In C.A.~Kamm et al.\ (Eds.), {\em Neural Networks for Signal
Processing III} (Proc. of the 1993 IEEE-SP Workshop, Baltimore, Maryland,
USA, September 1993). IEEE Press, New York 1993, pp. 321-330.
  
\bibitem{Driessel87}
K.R.~Driessel.
``On Finding the Eigenvalues and Eigenvectors of a Matrix by
Means of an Isospectral Gradient Flow''.
{\em Technical Report 541}, Department of Mathematical Science, 
Clemson University, Clemson, NC, 1987.

\bibitem{Duda73}
R.O.~Duda and P.E.~Hart.
{\em ``Pattern Classification and Scene Analysis''}.
John Wiley, New York, 1973.
 
\bibitem{Foldiak89}
P.~F\"oldi\'ak.
``Adaptive Network for Optimal Linear Feature Extraction''.
In {\em Proc. of the Int. Joint Conf. on Neural Networks}, 
Washington DC, 1989, pp. I-401-406.
 
\bibitem{Foldiak90}
P.~F\"oldi\'ak.
``Forming Sparse Representations by Local Anti-Hebbian Learning''.
In {\em Biological Cybernetics}, vol. 64, 1990, pp. 165-170.
 
\bibitem{Foldiak91}
P.~F\"oldi\'ak.
``Learning Invariance from Transformation Sequences''.
{\em Neural Computation}, vol. 3, 1991, pp. 194-200.

\bibitem{Freisleben93}
B.~Freisleben.
``PCA in a Network with Full Lateral Connections''.
Abstract In {\em Proc. Int. Conf. on Artificial Neural Networks (ICANN'93)},
Amsterdam, September 1993. Springer-Verlag, 1993, p. 618.
 
\bibitem{Fyfe93a}
C.~Fyfe.
``PCA Properties of Interneurons''.
In {\em Proc. Int. Conf. on Artificial Neural Networks (ICANN'93)},
Amsterdam, September 1993. Springer-Verlag, 1993, pp. 183-188.

\bibitem{Fyfe93b}
C.~Fyfe.
``A Simple, Homogeneous Parallel PCA Network''.
In {\em Proc. Int. J. Conf. on Neural Networks}, Nagoya, Japan, October
1993, pp. 2496-2499.
 
\bibitem{Gerbrands81}
J.J.~Gerbrands.
``On the Relationships Between SVD, KLT and PCA''.
{\em Pattern Recognition}, vol. 14, 1981, pp. 375-381.

\bibitem{Ghaloum91}
S.~Ghaloum and M.R.~Azimi-Sadjadi.
``Terrain Classification in SAR Images Using Principal Components
Analysis and Neural Networks''.
In {\em Proc. Int. J. Conf. on Neural Networks}, Singapore, November 1991,
vol. 3, pp. 2390-2395. 

\bibitem{Golub89}
G.H.~Golub and C.F.~Van Loan.
{\em Matrix Computations}, 2nd ed.\
Johns Hopkins University Press, Baltimore, 1989.
 
\bibitem{Gourlay73}
A.R.~Gourlay and G.A.~Watson.
{\em Computational Methods for Matrix Eigenproblems}.
John Wiley, New York, 1973.
 
\bibitem{Hammerstrom90}
D.~Hammerstrom, T.~Leen, and E.~Means.
``Dynamic and VLSI Implementation of Self-Organizing Networks''.
In R.~Eckmiller (Ed.), {\em Advanced Neural Computers},
North-Holland, Amsterdam, 1990, pp. 185-192.

\bibitem{Hasler92}
P.~Hasler and L.~Akers.
``Circuit Implementation of a Trainable Neural Network Using the Generalized
Hebbian Algorithm with Supervised Techniques''.
In {\em Proc. Int. J. Conf. on Neural Networks}, Baltimore, Maryland,
June 1992, vol. I, pp.160-165.

\bibitem{Hebb49}
D.O.~Hebb.
{\em The Organization of Behavior}.
John Wiley, New York, 1949.

\bibitem{Hertz91}
J.~Hertz, A.~Krogh, and R.G.~Palmer.
{\em Introduction to the Theory of Neural Computation}.
Addison-Wesley, New York, 1991.

\bibitem{Heskes91}
T.~Heskes, B.~Kappen, and S.~Gielen.
``Neural Networks Learning in a Changing Environment''.
In T. Kohonen et al. (Eds.), {\em Artificial Neural Networks}
(Proc. ICANN'91, Espoo, Finland, June 1991).
North-Holland, Amsterdam, 1991, pp. 15-20.
 
\bibitem{Hornik92}
K.~Hornik and C.-M.~Kuan.
``Convergence Analysis of Local Feature Extraction Algorithms''.
{\em Neural Networks}, vol. 5, 1992, pp. 229-240.

\bibitem{Hotelling33}
H.~Hotelling.
``Analysis of a Complex of Statistical Variables into Principal Components''.
{\em J. Educ. Psych.}, vol. 24, 1933, pp. 498-520.
 
\bibitem{Hrycej89a}
T.~Hrycej.
``A Non-Competitive Model for Unsupervised Learning''.
In {\em  Proc. of First IEE Int. Conf. on Neural Networks},
London, 1989, pp. 233-237.

\bibitem{Hrycej89b}
T.~Hrycej.
``Unsupervised Learning by Backward Inhibition''.
In {\em Proc. Int. J. Conf. on Artificial Intelligence}, Detroit, 1989,
pp. 170-175.

\bibitem{Hrycej90}
T.Hrycej.
``Self-Organization by Delta Rule''.
In {\em Proc. Int. J. Conf. on Neural Networks},
San Diego, June 1990, pp. II-307-312.

\bibitem{Hrycej92}
T.~Hrycej.
``Supporting Supervised Learning by Self-Organization''.
{\em Neurocomputing}, vol. 4, 1992, pp. 17-30.

\bibitem{Hyman91}
S.D.~Hyman, T.P.~Vogl, K.T.~Blackwell, G.S.~Barbour, J.M.~Irvine, and
D.L.~Alkon.
``Classification of Japanese Kanji Using Principal Component Analysis as
a Preprosessor to an Artificial Neural Networks''.
In {\em Proc. Int. J. Conf. on Neural Networks}, Seattle, Washington,
July 1991, vol. I, pp. 233-238.

\bibitem{Intrator92}
N.~Intrator.
``Feature Extraction Using an Unsupervised Neural Network''.
{\em Neural Computation}, vol. 4, 1992, pp. 98-107.
 
\bibitem{Jolliffe86}
I.T.~Jolliffe. 
{\em Principal Component Analysis.}
Springer-Verlag, New York, 1986.

\bibitem{Joutsensalo93}
J.~Joutsensalo and J.~Karhunen.
``Nonlinear Multilayer Principal Component Type Subspace
Learning Algorithms''.
In C.A.~Kamm et al.\ (Eds.), {\em Neural Networks for Signal
Processing III} (Proc. of the 1993 IEEE-SP Workshop, Baltimore, Maryland,
USA, September 1993). IEEE Press, New York 1993, pp. 68-77.

\bibitem{Jutten91}
C.~Jutten and J.~Herault.
``Blind Separation of Sources, Part I: an Adaptive Algorithm Based on
Neuromimetic Architecture''. Signal Processing, vol. 24, 1991, pp. 1-10.

\bibitem{Karhunen82}
J.~Karhunen.
``On the Recursive Estimation of the Eigenvectors of
Correlation Type Matrices'' (in Finnish).
{\em Lic. Tech. Thesis}, Helsinki University of Technology,
Finland, 1982.

\bibitem{Karhunen84a}
J.~Karhunen.
``Adaptive Algorithms for Estimating Eigenvectors of
Correlation Type Matrices''.
In {Proc. IEEE Int. Conf. Acoustics, Speech, and Signal
Processing}, San Diego, Calif., March 1984, pp. 14.6.1-14.6.4.

\bibitem{Karhunen84b}
J.~Karhunen.
``Recursive Estimation of Eigenvectors of Correlation Type 
Matrices for Signal Processing Applications''.
{\em Dr. Tech. Thesis}, Helsinki University of Technology, Finland, 1984.

\bibitem{Karhunen85}
J.~Karhunen.
``Simple Gradient Type Algorithms for Data-Adaptive Eigenvector Estimation''.
Helsinki Univ. of Technology, Dept. of Technical Physics. Report A584, 1985.

\bibitem{Karhunen91a}
J.~Karhunen and J.~Joutsensalo.
``Tracking of Sinusoidal Frequencies by Neural Network Learning Algorithms''.
In {\em Proc. IEEE Int. Conf. Acoustics, Speech, and Signal
Processing}, Toronto, Canada, May 1991, pp. 3177-80. 

\bibitem{Karhunen91b}
J.~Karhunen and J.~Joutsensalo.
``Frequency Estimation by a Hebbian Subspace Learning Algorithm''.
In T. Kohonen et al. (Eds.), {\em Artificial Neural Networks}
(Proc. ICANN'91, Espoo, Finland, June 1991).
North-Holland, Amsterdam, 1991, pp. 1637-1640.

\bibitem{Karhunen92b}
J.~Karhunen and J.~Joutsensalo.
``Learning of Sinusoidal Frequencies by Nonlinear Constrained
Hebbian Algorithms''.
In S.Y.~Kung et al.\ (Eds.), {\em Neural Networks for Signal
Processing II} (Proc. of the 1992 IEEE-SP Workshop, Copenhagen, Denmark,
August-September 1992). IEEE Press, New York 1992, pp. 39-48.

\bibitem{Karhunen92b}
J.~Karhunen and J.~Joutsensalo.
``Nonlinear Hebbian Algorithms for Sinusoidal Frequency Estimation''.
In I.~Aleksander and J.~Taylor (Eds.) {\em Artificial Neural
Networks, 2} (Proc. ICANN'92, Brighton, United Kingdom, September 1992).
North-Holland, Amsterdam, 1992, pp. 1099-1102.

\bibitem{Karhunen93a}
J.~Karhunen and J.~Joutsensalo.
``Representation and Separation of Signals Using Nonlinear
PCA Type Learning''.
To appear in {\em Neural Networks}.

\bibitem{Karhunen93b}
J.~Karhunen and J.~Joutsensalo.
``Learning of Robust Principal Component Subspace''.
In {\em Proc. Int. Joint Conf. Neural Networks}, Nagoya, Japan,
October 1993, pp. 2409-2412.

\bibitem{Karhunen93c}
J.~Karhunen and J.~Joutsensalo.
``Nonlinear Generalizations of Principal Component Learning Algorithms''.
In {\em Proc. Int. Joint Conf. Neural Networks}, Nagoya, Japan,
October 1993, pp. 2599-2602.

\bibitem{Karhunen93d}
J.~Karhunen.
``Stability of Oja's PCA Subspace Rule''.
To appear in {\em Neural Computation}.

\bibitem{Karhunen46}
K.~Karhunen.
``Zur Spektraltheorie stochastischer Prozesse''.
{\em Ann. Acad. Sci. Fennicae}, 34, 1946.
 
\bibitem{Kittler78}
J.~Kittler.
``The subspace approach to pattern recognition''.
In R.~Trappl, G.J.~Klir, and L.~Ricciardi (Eds.), {\em Progress in
Cybernetics and Systems Research}. Hemisphere Publ. Co., Washington, 1978.
 
\bibitem{Kohonen77}
T.~Kohonen.
{\em Associative Memory - a System - Theoretical Approach},
Springer-Verlag, 1977.

\bibitem{Kohonen89}
T.~Kohonen.
{\em Self-Organization and Associative Memory}, 3rd ed.\
Springer-Verlag, 1989.

\bibitem{Kotilainen92}
P.~Kotilainen, J.~Saarinen, and K.~Kaski.
``Hardware Implementations of PCA Networks''.
In I.~Aleksander and J.~Taylor (Eds.) {\em Artificial Neural
Networks, 2} (Proc. ICANN'92, Brighton, United Kingdom, September 1992).
North-Holland, Amsterdam, 1992, pp. 1427-1430.

\bibitem{Kotilainen93}
P.~Kotilainen.
``Simulations and Implementations of Neural Networks for
Principal Component Analysis''.
{\em Lic. Tech. thesis}, Tampere Univ. of Tech., Electronics Lab., Report
4-93, Finland, 1993.
 
\bibitem{Krogh90}
A.~Krogh and J.A.~Hertz.
``Hebbian Learning of Principal Components''. 
In R.~Eckmiller, G.~Hartmann, and F.~Hauske (Eds.), {\em Parallel Processing
in Neural Systems and Computers}. Elsevier (North-Holland), Amsterdam,
1990, pp. 183-186.

\bibitem{Kuan91}
C.M.~Kuan and K.~Hornik.
``Convergence of Learning Algorithm with Constant Learning Rates''.
{\em IEEE Trans. on Neural Networks}, vol. 2, 1991, pp. 484-489.

\bibitem{Kuhnel90}
H.~K\"uhnel and P.~Tavan.
``The Anti-Hebb Rule Derived from Information Theory''.
In R.~Eckmiller, G.~Hartmann and H.~Hauske (Eds.), {\em Parallel
Processing in Neural Systems and Computers}, North-Holland, 
Amsterdam, 1990, pp. 187-190.

\bibitem{Kung90a}
S.Y.~Kung.
``Orthogonal Learning Network for Constrained Principal Component Problem''.
In {\em Proc. Int. Joint Conf. on Neural Networks}, San Diego,
California, 1990, pp. I-441-449.

\bibitem{Kung90b}
S.Y.~Kung and K.I.~Diamantaras.
``A Neural Network Learning Algorithm for Adaptive Principal
Component EXtraction (APEX)''.
In {\em Proc. IEEE Int. Conf. on Acoustics, Speech, and Signal Processing},
Albuquerque, New Mexico, April 1990, pp. 861-864.
 
\bibitem{Kung90c}
S.Y.~Kung.
``Adaptive Principal Component Analysis via an Orthogonal Learning Network''.
In {\em Proc. IEEE Int. Symp. on Circuits and Systems}, New Orleans, USA,
May 1990, pp. 719-722.
 
\bibitem{Kung91}
S.Y.~Kung and K.I.~Diamantaras.
``Neural Networks for Extracting Unsymmetric Principal Components''.
In B.H.~Juang, S.Y.~Kung, and C.A.~Kamm (Eds.), {\em Neural
Networks for Signal Processing} (Proc. 1991 IEEE-SP Workshop, Princeton,
NJ). IEEE Press, New York, 1991, pp. 50-59.
 
\bibitem{Kung91b}
S.Y.~Kung, K.I.~Diamantaras, and J.S.~Taur.
``Neural Networks for Extracting Pure / Constrained / Oriented
Principal Components''.
In R.J.~Vaccaro (Ed.), {\em SVD and Signal Processing, II: Algorithms,
Analysis and Applications}. Elsevier, 1991.
 
\bibitem{Kung93}
S.Y.~Kung.
{\em Digital Neural Networks}. Prentice-Hall, 1993.

\bibitem{Kushner78}
H.J.~Kushner and D.S.~Clark.
{\em Stochastic Approximation Methods for Constrained and
Unconstrained Systems}.
Springer-Verlag, New York, 1978.
 
\bibitem{Kushner81}
H.J.~Kushner and H.~Huang.
``Asymptotic Properties of Stochastic Approximations with Constant
Coefficients''.
{\em SIAM J. of Control and Optimization}, vol. 19, 1981, pp. 87-105.
 
\bibitem{Leen90}
T.K.~Leen et al.
``Hebbian Feature Discovery Improves Classifier Efficiency''.
In {\em Proc. Int. J. Conf. on Neural Networks}, San Diego, California,
June 1990, vol. I, pp. 51-56.

\bibitem{Leen91}
T.K.~Leen.
``Dynamics of Learning in Linear Feature-Discovery Networks''.
{\em Network}, vol. 2, 1991, pp. 85-105.

\bibitem{Lenz91}
R.~Lenz and M. \"Osterberg.
``A Parallel Learning Filter System That Learns the KL-expansion
from Examples''.
In B.H.~Juang, S.Y.~Kung, and C.A.~Kamm (Eds.), {\em Neural
Networks for Signal Processing} (Proc. 1991 IEEE-SP Workshop, Princeton,
NJ). IEEE Press, New York, 1991, pp. 121-130. 

\bibitem{Lenz92a}
R.~Lenz and M. \"Osterberg.
``Computing the Karhunen-Loeve Expansion with a Parallel, Unsupervised
Filter System''.
{\em Neural Computation}, vol. 4, 1992, pp. 382-392.

\bibitem{Lenz92b}
R.~Lenz and M. \"Osterberg.
``A New Method for Unsupervised Linear Feature Extracting, Using
Fourth Order Moments''.
{\em Proc. of the 11th IAPR Int. Conf. on Pattern Recognition},
Hague, Netherlands, 1992, vol. II, pp. 71-74.

\bibitem{Lin93}
S.~Lin and Q.Y.~Yin.
``Adaptive Principal Component Analysis via Neural Network''.
In {\em Proc. Int. Conf. on Signal Processing(?) (ICSP93)}, Beijing,
China, October 1993, pp. 1224-1227.

\bibitem{Linsker86a}
R.~Linsker.
``From Basic Network Principles to Neural Architectures: Emergence of
Spatial-Opponent Cells''.
In {\em Proc. National Academy of Science, USA, Neurobiology},
vol. 83, 1986, pp. 7508-7512.

\bibitem{Linsker86b}
R.~Linsker.
``From Basic Network Principles to Neural Architectures: Emergence of
Orientation-Selective Cells''.
In {\em Proc. National Academy of Science, USA, Neurobiology},
vol. 83, 1986, pp. 8390-8394.

\bibitem{Linsker86c}
R.~Linsker.
``From Basic Network Principles to Neural Architectures: Emergence of
Orientation Columns''.
In {\em Proc. National Academy of Science, USA, Neurobiology},
vol. 83, 1986, pp. 8779-8783.

\bibitem{Linsker88a}
R.~Linsker.
``Self-Organization in a Perceptual Network''.
{\em IEEE Computer Magazine}, vol. 21, March 1988, pp. 105-117.
 
\bibitem{Linsker88b}
R.~Linsker.
``Designing A Sensory Processing System:
What Can Be Learned From Principal Components Analysis?''.
{\em Proc. of Int. Joint Conf. on Neural Networks}, 1990, pp. II-291-297.

\bibitem{Linsker92}
R.~Linsker.
``Local Synaptic Learning Rules Suffice to Maximize Mutual Information
in a Linear Network''.
{\em Neural Computation}, vol. 4, 1992, pp. 691-702.

\bibitem{Ljung77}
L.~Ljung.
``Analysis of Recursive Stochastic Algortihms''.
{\em IEEE Trans. on Automatic Control}, vol. 22, August 1977, pp. 551-575.
 
\bibitem{MacKay90}
D.C.~MacKay and K.D.~Miller.
''Analysis of Linsker's Simulations of Hebbian Rules''.
{\em Neural Computation}, vol. 2, 1990, pp. 173-187.

\bibitem{Malki91}
H.A.~Malki and A.~Moghaddamjoo.
``Using the Karhunen-Lo\'eve Transformation in the 
Back-Propagation Training Algorithm''.
{\em IEEE Trans. on Neural Networks}, vol. 2, January 1991, pp. 162-165.

\bibitem{Martinelli92}
G.~Martinelli, L.~Prina Ricotti, and G.~Marcone.
``Neural Clustering for Optimal KLT Image Compression''.
{\em IEEE Trans. on Signal Processing}, vol. 41, 1993, pp. 1737-1739.
 
\bibitem{Nagasaka93}
Y.~Nagasaka and A.~Iwata.
``Performance Evaluation of BP and PCA Neural Networks for ECG Data
Compression''.
In {\em Proc. Int. Joint Conf. Neural Networks}, Nagoya, Japan,
October 1993, pp. 1003-1006.
 
\bibitem{Ogawa92}
H.~Ogawa.
``Karhunen-Loeve Subspace''.
{\em Proc. of the 11th IAPR Int. Conf. on Pattern Recognition},
Hague, Netherlands, August 1993, vol. II, pp. 75-78.

\bibitem{Oja82a}
E.~Oja.
``A Simplified Neuron Model as a Principal Component Analyzer''.
{\em J. of Mathematical Biology}, vol. 16, 1982, pp. 267-273.

\bibitem{Oja82b}
E.~Oja and J.~Karhunen.
``New Methods for Stochastic Approximation of Truncated Karhunen -
Loeve Expansions''. In {\em Proc. 6th Int. Conf. on Pattern
Recognition}, Munich, Oct. 1982, pp. 134 - 137.

\bibitem{Oja83a}
E.~Oja.
{\em Subspace Methods for Pattern Recognition}.
Research Studies Press and J. Wiley, Letchworth, England,
1983.

\bibitem{Oja83b}
E.~Oja and M.~Kuusela.
``The ALSM Algorithm - an Improved Subspace Method of
Classification''. {\em Pattern Recognition}, vol. 16, 1983, pp.
421-427.

\bibitem{Oja85}
E.~Oja and J.~Karhunen. 
``On Stochastic Approximation of the Eigenvectors and Eigenvalues of 
the Expectation of a Random Matrix''. 
{\em J. of Math. Analysis and Applications}, vol. 106, 1985, pp. 69-84.

\bibitem{Oja87}
E.~Oja and J.~Parkkinen.
``Texture Subspaces''. In P.A.~Devijver and J.~Kittler (Eds.), 
{\em Pattern Recognition Theory and Applications}, Springer-Verlag,
Berlin, 1987, pp. 21-34.

\bibitem{Oja88}
E.~Oja and T.~Kohonen.
``The Subspace Learning Algorithm as a Formalism for Pattern Recognition
and Neural Networks''.
In {\em Proc. IEEE Int. Conf. on Neural Networks}, San Diego, July 1988,
pp. 277-284. Reprinted in P.~Mehra and B.W.~Wah (Eds.), {\em
Artificial Neural Networks: Concepts and Theory}, IEEE Computer
Society Press, 1992, pp. 101 - 108. 
 
\bibitem{Oja89}
E.~Oja.
``Neural Networks, Principal Components, and Subspaces''.
{\em Int. J. of Neural Systems},  vol. 1, 1989, pp. 61-68.

\bibitem{Oja91a}
E.~Oja, H.~Ogawa, and J.~Wangviwattana.
``Learning in nonlinear constrained Hebbian networks''.
In T. Kohonen et al.\ (Eds.), {\em Artificial Neural Networks} (Proc.
ICANN'91, Espoo, Finland, June 1991). North-Holland, Amsterdam, 1991,
pp. 385-390.

\bibitem{Oja91b}
E.~Oja.
``Data Compression, Feature Extraction, and Autoassociation in
Feedforward Neural Networks''. 
In T. Kohonen et al.\ (Eds.), {\em Artificial Neural Networks} (Proc.
ICANN'91, Espoo, Finland, June 1991). North-Holland, Amsterdam, 1991,
pp. 737 - 745.

\bibitem{Oja92a}
E.~Oja.
``Principal Components, Minor Components, and Linear Neural Networks''.
{\em Neural Networks}, vol. 5, 1992, pp. 927-936.

\bibitem{Oja92b}
E.~Oja, H.~Ogawa, and J.~Wangviwattana.
``PCA in Fully Parallel Neural Networks''.
In I.~Aleksander and J.~Taylor (Eds.) {\em Artificial Neural
Networks, 2} (Proc. ICANN'92, Brighton, United Kingdom, September 1992).
North-Holland, Amsterdam, 1992, pp. 199-202.

\bibitem{Oja92c}
E.~Oja, H.~Ogawa, and J.~Wangviwattana.
``Principal Component Analysis by Homogeneous Neural Networks, Part I:
the Weighted Subspace Criterion''.
{\em IEICE Trans. on Information and Systems (Japan)}, vol. E75-D,
1992, pp. 366 - 375.

\bibitem{Oja92d}
E.~Oja, H.~Ogawa, and J.~Wangviwattana.
``Principal Component Analysis by Homogeneous Neural Networks, Part II:
Analysis and Extensions of the Learning Algorithms''.
{\em IEICE Trans. on Information and Systems (Japan)}, vol. E75-D,
1992, pp. 376-382.

\bibitem{Oja93a}
E.~Oja.
``A Nonlinear Symmetrical PCA Network Learns True Principal Components''.
{\em Research Report 40}, Lappeenranta Univ. of Technology, Dept. of
Information Technology, 1993.

\bibitem{Oja93b}
E.~Oja and J.~Karhunen.
``Nonlinear PCA: Algorithms and Applications''.
Helsinki Univ. of Technology, Lab. of Computer and Inform. Science,
Report A18, September 1993. (Abstract in {\em Proc. WCNN'93},
Portland, Oregon, July 1993, p. II-396).

\bibitem{Palmieri91a}
F.~Palmieri and J.~Zhu.
``A Comparison of Two Eigen-Networks''.
{\em Proc. of the Int. J. Conf. on Neural Networks}, Seattle, WA, 1991,
vol. 2, pp. 193-199.

\bibitem{Palmieri91b}
F.~Palmieri and J.~Zhu.
``Linear Neural Networks Which Minimize the Output Variance''.
{\em Proc. of the Int. J. Conf. on Neural Networks}, Seattle, WA, 1991,
vol. 1, pp. 791-797.

\bibitem{Palmieri92a}
F.~Palmieri.
``A Self-Organizing Neural Network for Nonlinear Filtering''. 
{\em Proc. of the Int. Symp. on Circuits and Systems}, San Diego,
California, May 1992.

\bibitem{Palmieri92b}
F.~Palmieri.
``A Self-Organizing Neural Network for Multidimensional Approximation''. 
{\em Proc. of the Int. Conf. on Neural Networks}, Baltimore, Maryland,
June 1992, pp. IV-802-807.

\bibitem{Palmieri93a}
F.~Palmieri.
``Linear Self-Association for Universal Memory and Approximation''.
{\em Proc. of the World Congress of Neural Networks}, Portland, 
Oregon, July 1993, pp. II-339-343.

\bibitem{Palmieri93b}
F.~Palmieri, J.~Zhu, and C.~Chang.
``Anti-Hebbian Learning in Topologically Constrained Linear Networks:
A Tutorial''.
To appear in {\em IEEE Trans. on Neural Networks}.

\bibitem{Palmieri93c}
F.~Palmieri and J.~Zhu.
``Hebbian Learning in Linear Neural Networks: A Review''.
{\em Technical Report 5/93}, Dept. of Electrical and Systems Eng., The
Univ. of Connecticut, Storrs, Connecticut, 1993. 57p.

\bibitem{Parlett80}
B.N.~Parlett.
{\em The Symmetric Eigenvalue Problem}.
Prentice Hall, Englewood Cliffs, NJ, 1980.
 
\bibitem{Perkins90}
J.E.~Perkins, U.~Helmke and J.B.~Moore.
``Balanced Realization via Gradient Flow Techniques''.
{\em Systems and Control Letters}, vol. 14, 1990, pp. 369-380.
 
\bibitem{Plumbley91}
M.D.~Plumbley.
``On Information Theory and Unsupervised Neural Networks''.
{\em Technical Report CUED/F-INFENG/TR.78}. Cambridge Univ.,
Engineering Dept., United Kingdom, 1991. 81p.

\bibitem{Plumbley92}
M.D.~Plumbley.
``Information Theory and Neural Network Learning Algorithms''.
In {\em Neural Computing Research and Applications: Part One}.
Queen's Univ. at Belfast, Northern Ireland, June 1992, pp. 145-155.
 
\bibitem{Plumbley93a}
M.D.~Plumbley.
``Approximating Optimal Information Transmission Using Local Hebbian 
Algorithms in a Double Feedback Loop''.
In {\em Proc. Int. Conf. on Artificial Neural Networks (ICANN'93)},
Amsterdam, September 1993. Springer-Verlag, 1993, pp. 435-440.
 
\bibitem{Plumbley93b}
M.D.~Plumbley.
``Efficient Information Transfer and Anti-Hebbian Neural Networks''.
{\em Neural Networks}, vol. 6, 1993, pp. 823-833.

\bibitem{Plumbley93c}
M.D.~Plumbley.
``A Hebbian/Anti-Hebbian Network Which Optimizes Information
Capacity by Orthonormalizing the Principal Subspace''.
In {\em Proc. of the IEE Conf. on Artificial Neural Networks},
Brighton, United Kingdom, May 1993, pp. 86-90.

\bibitem{Polycarpou92}
M.P.~Polycarpou and P.A.~Ioannou.
``Learning and Convergence Analysis of Neural-type Structured Networks''.
{\em IEEE Trans. on Neural Networks}, vol. 3, 1992, pp. 39-50.

\bibitem{Pomierski93}
T.~Pomierski, H.M.~Gross, and D.~Wendt.
``A Distributed Multicolumnar System for Primary Cortical Analysis
of Real-World Scenes''.
In {\em Proc. Int. Conf. on Artificial Neural Networs (ICANN'93)}.
Springer-Verlag, Amsterdam, September 1993, pp. 142-147.

\bibitem{Rayner89}
P.~Rayner and M.R.~Lynch.
``A New Connectionist Model Based on A Non-Linear Adaptive Filter''.
{\em Proc. of IEEE Int. Conf. on Acoustics, Speech, and Signal
Processing}, April 1989.
 
\bibitem{Rubner89}
J.~Rubner and P.~Tavan.
``A Self-Organizing Network for Principal Component Analysis''.
{\em Europhysics Letters}, vol. 10, 1989, pp. 693-698.

\bibitem{Rubner90a}
J.~Rubner and K.~Schulten.
``Development of Feature Detectors by Self-Organization''.
{\em Biological Cybernetics}, vol. 62, 1990, pp. 193-199.

\bibitem{Rubner90b}
J.~Rubner, K.~Schulten, and P.~Tavan.
``A Self-Organizing Network for Complete Feature Extraction''.
In R.~Eckmiller, G.~Hartmann, and F.~Hauske (Eds.), {\em Parallel
Processing in Neural Systems and Computers}. North-Holland, Amsterdam
1990, pp. 365-368.

\bibitem{Russo91}
L.~Russo.
``An Outer Product Neural Network for Extracting Principal 
Components from a Time Series''. 
In B.H.~Juang et.al. (Eds.), {\em Neural Networks for Signal 
Processing} (Proc. of the 1991 IEEE-SP Workshop). IEEE Press, New York,
1991, pp. 161-170.

\bibitem{Russo92}
L.~Russo and E.C.~Real. 
``Image Compression Using an Outer Product Neural Network''.
{\em Proc. of IEEE Int. Conf. Acoustics, Speech, and Signal Processing},
San Francisco, March 1992, pp. II-377-380.

\bibitem{Sanger89a}
T.D.~Sanger.
``An Optimality Principle for Unsupervised Learning''.
In D.S.~Touretzky (Ed.), {\em Advances in Neural Information
Processing Systems}, vol. 1. Morgan Kaufmann, Palo Alto, CA, 1989, pp. 11-19.
 
\bibitem{Sanger89b}
T.D.~Sanger.
``Optimal Unsupervised Learning in a Singer-Layer Linear Feedforward
Neural Network''.
{\em Neural Networks}, vol. 2, 1989, pp. 459-473.

\bibitem{Sanger90}
T.D.~Sanger. 
``Analysis of the Two-Dimensional Receptive Fields Learned by
the Generalized Hebbian Algorithm in Response to Random Input''.
{\em Biological Cybernetics}, vol. 63, 1990, pp. 221-228.

\bibitem{Sanger91}
T.D.~Sanger.
``Optimal Hidden Units for Two-layer Nonlinear Feedforward
Neural Networks''.
{\em Int. Journal of Pattern Recognition and Artificial Intelligence},
vol. 5, 1991, pp. 545-561.

\bibitem{Saund89}
E.~Saund.
``Dimensionality-Reduction Using Connectionist Networks''.
{\em IEEE Trans. on Pattern Analysis and Machine Intelligence}, vol. 11,
March 1989, pp. 304-314.
 
\bibitem{Shapiro92}
J.L.~Shapiro, and A.~Pr\"ugel-Bennett.
``Unsupervised Hebbian Learning and the Shape of the Neuron
Activation Function''.
In I.~Aleksander and J.~Taylor (Eds.) {\em Artificial Neural
Networks, 2} (Proc. ICANN'92, Brighton, United Kingdom, September 1992).
North-Holland, Amsterdam, 1992, pp. 179-182.

\bibitem{Shapiro93}
J.L.~Shapiro, and A.~Pr\"ugel-Bennett.
``Competitive Networks of Non-Linear Hebbian Neurons''. In {\em Proc.
WCNN}, Portland, Oregon, July 1993, pp. II435 - 438.

\bibitem{Sicuranza90}
Sicuranza, Ramponi, and Marsi.
``Artificial Neural Networks for Image Compression''.
{\em Electronics Letters}, vol. 26, 1990, pp. 477-479.

\bibitem{Silva90}
F.M.~Silva and L.B.~Almeida.
``Acceleration Techniques for the Backpropagation Algorithm''.
In  L.B.~Almeida and C.~Wellekens (Eds.), {\em Neural Networks, Proc.
EURASIP Workshop}, Springer-Verlag, 1990.

\bibitem{Silva91a}
F.M.~Silva and L.B.~Almeida.
``A Distributed Decorrelation Algorithm''.
In E.~Gelenbe (Ed.), {\em Neural Networks: Advances and Applications}. 
North-Holland, Amsterdam, 1991, pp. 145-163.

\bibitem{Silva91b}
F.M.~Silva and L.B.~Almeida.
``A Distributed Solution for Data Orthonormalization''.
In T.~Kohonen et al. (Eds.), {\em Artificial Neural Networks} (Proc.
ICANN'91, Espoo, Finland, June 1991). Elsevier, Amsterdam, 1991,
pp. 943-948.

\bibitem{Sirat89}
J.A.~Sirat, J.R.~Viala, and C.~Remus.
``Image compression with competing multilayer perceptron''.
In {\em Proc. of First IEE Int. Conf. on Neural Networks},
London, 1989, pp. 404-408.

\bibitem{Sirat91}
J.A.~Sirat.
``A Fast Neural Algorithm for Principal Component
Analysis and Singular Value Decomposition.
{\em Int. J. of Neural Systems}, vol. 2, 1991, pp. 147-155. 

\bibitem{Smith91}
D.S.~Smith.
``Dynamical Systems That Perform the Singular Value Decomposition''.
{\em System and Control Letters}, vol. 15, 1991, pp. 319-327.

\bibitem{Softky91}
W.R.~Softky and D.M.~Kammen.
``Correlation in High Dimensional or Asymmetric Data Sets: 
Hebbian Neuronal Processing''.
{\em Neural Networks}, vol. 4, 1991, pp. 337-347.

\bibitem{Takahashi93}
T.~Takahashi.
``Principal Component Analysis is a Group Action of SO(N) Which Minimizes
an Entropy Function''.
In {\em Proc. Int. J. Conf. on Neural Networks}, Nagoya, Japan,
October 1993, pp. 355-358.

\bibitem{Taur91}
J.S.~Taur and S.Y.~Kung.
``Comparison of Several Learning Subspace Methods for
Classification''.
In {\em Proc. ICASSP-91}, Toronto, Canada, May 1991, pp. 1069-1072.

\bibitem{Taylor93}
J.G.~Taylor and S.G.~Coombes.
``Learning Hogher Order Correlations''.
{\em Neural Networks}, vol. 6, 1993, pp. 423-427.

\bibitem{Uosaki93}
K.~Uosaki.
``A Hybrid Neural Network for Principal Component Analysis''.
In {\em Proc. Int. J. Conf. on Neural Networks}, Nagoya, Japan,
October 1993, pp. 2500-2503.
 
\bibitem{Vandewalle91}
J.~Vandewalle and B.~De Moor.
``On the Use of the Singular Value Decomposition in Identification
and Signal Processing''.
In G.H.~Golub and P.~Van Doren (Eds.), {\em Numerical Linear Algebra,
Digital Signal Processing and Parallel Algorithms}. Springer-Verlag, 
Berlin, 1991, pp. 321-343.
 
\bibitem{Vaucher93}
G.~Vaucher.
``Study of a Self-Learning Artificial Neuron Model''.
In S.~Gielen and B.~Kappen (Eds.), {\em ICANN'93 (Proc. Int. Conf.
on Artificial Neural Networks, Amsterdam, September 1993)}.
Springer-Verlag, London 1993, p. 204.

\bibitem{Vogl91}
T.P.~Vogl, K.T.~Blackwell, S.D.~Hyman, G.S.~Barbour, and D.L.~Alkon.
``Classification of Handwritten Digits and Japanese Kanji''.
In {\em Proc. Int. J. Conf. on Neural Networks}, Seattle, Washington,
July 1991, vol. I, pp. 97-102.
 
\bibitem{Lwang92}
L.~Wang and J.~M.~Mendel.
``Parallel Structured Networks for Solving a Wide Variety
of Matrix Algebra Problems''.
{\em Journal of Parallel and Distributed Computing}, vol. 14, 1992,
pp. 236-247.

\bibitem{Wang93a}
L.-Y.~Wang and E.~Oja.
``Robust fitting by nolinear neuron units''
In {\em Proc. 8th Scandinavian Conf. on Image Analysis}, Tromso.
Norway, May 1993, pp. 531-537.

\bibitem{Wang93b}
L.-Y.~Wang and E.~Oja.
``Image Compression by MLP and PCA Neural Networks''.
In {\em Proc. 8th Scandinavian Conf. on Image Analysis}, Tromso.
Norway, May 1993, pp. 1317-1324.

\bibitem{Wang93c}
L.-Y.~Wang and E.~Oja.
``Constrained Anti-Hebbian Learning for Curve and Surface Fitting''.
In {\em Proc. Int. Conf. on Signal Processing(?) (ICSP'93)}. Beijing, China, 
October 1993, pp. 1163-1166.

\bibitem{Watanabe65}
S.~Watanabe.
``Karhunen-Lo\`{e}ve expansion and factor analysis''.
In {\em Trans. 4th Prague Conf. Inform. Theory, Stat. Decision
Functions, and Random Proc.}, Prague, 1965, pp. 635-660.

\bibitem{Watkins89}
D.S.~Watkins and L.~Elsner.
``Self Equivalent Flows Associated with the Singular Value Decomposition''.
{\em SIAM J. Matrix Anal. Appl.}, vol. 10, 1989, pp. 224-258.
 
\bibitem{White92}
R.H.~White.
``Competitive Hebbian Learning: Algorithm and Demonstrations''.
{\em Neural Networks}, vol. 5, 1992, pp. 261-275.

\bibitem{Williams85}
R.J.~Williams.
``Feature Discovery Through Error-Correction Learning''.
{\em Technical Report 8501}. Institute of Cognitive 
Science, University of California, San Diego, CA, 1985.

\bibitem{Xu91a}
L.~Xu. 
``Least MSE Reconstruction for Self-Organization''.
In {\em Proc. Int. J. Conf. on Neural Networks}, Singapore, November 1991,
pp. 2362-2367 (part I) and pp. 2368-2373 (part II).

\bibitem{Xu91b}
L.~Xu, A.~Krzyzak, and E.~Oja.
``Neural Networks for Dual Subspace Pattern Recognition Method''.
{\em Int. J. Neural Systems}, vol. 2, 1991, pp. 169 - 184.

\bibitem{Xu92a}
L.~Xu, E.~Oja, and C.Y.~Suen.
``Modified Hebbian Learning for Curve and Surface Fitting''.
{\em Neural Networks}, vol. 5, 1992, pp. 441-457.
 
\bibitem{Xu92b}
L.~Xu and A.~Yuille. 
``Robust Principal Component Analysis by Self-Organizing
Rules Based on Statistical Physics Approach''.
{\em Harvard Robotics Laboratory: Technical Report}. No.92-3, February 1992.

\bibitem{Xu92c}
L.~Xu and A.~Yuille. 
``Robust PCA Learning Rules Based on Statistical Physics Approach''.
In {\em Proc. Int. J. Conf. on Neural Networks}, Baltimore, Maryland,
June 1992, pp. I-812-817.
 
\bibitem{Xu93a}
L.~Xu and A. Yuille.
``Self-Organizing Rules for Robust Principal Component Analysis''.
In S.J.~Hanson, J.D.~Cowan, and C.L.~Giles (Eds.), {\em Advances
in Neural Information Processing Systems 5}. Morgan Kaufmann, San Mateo, 
California 1993, pp. 467-474.

\bibitem{Xu93b}
L.~Xu.
``Least Mean Square Error Reconstruction Principle for Self-Organizing 
 Neural-Nets''.
{\em Neural Networks}, vol. 6, 1993, pp. 627-648. 
 
\bibitem{Xu93c}
L.~Xu.
``Robust Principal Component Analysis by Self-Organizing
Rules Based on Statistical Physics Approach''.
{\em IEEE Trans. on Neural Networks}, 1993, in press.

\bibitem{Xu93d}
L.~Xu and S.~Klasa.
``A PCA-Like Rule for Pattern Classification Based on Attributed Graph''.
In {\em Proc. Int. J. Conf. on Neural Networks}, Nagoya, Japan, October
1993, pp. 1281-1284.

\bibitem{Yang91}
J.~Yang and G.A.~Dumont.
``Classification of Acoustic Emission Signals via Hebbian Feature
Extraction''. 
In {\em Proc. Int. J. Conf. on Neural Networks}, Seattle, Washington,
July 1991, vol. I, pp. 113-118.

\bibitem{Yuille89}
A.L.~Yuille, D.M.~Kammen, and D.S.~Cohen.
``Quadrature and the Development of Orientation Selective Cortical Cells
by Hebb Rules''.
{\em Biological Cybernetics}, vol. 61, 1989, pp. 183-194.
  
\end{thebibliography}
%
\end{document}
